---
title: "Presentacion1"
author: "Santiago Figueroa"
date: "2024-11-06"
output:
  ioslides_presentation: default
  beamer_presentation: default
  slidy_presentation: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting
syntax for authoring HTML, PDF, and MS Word documents. For more details
on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that
includes both content as well as the output of any embedded R code
chunks within the document.

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Diapositiva de script

```{r}
compleja_lista <- list(
  numero = 42,
  vector = c(1, 2, 3),
  matriz = matrix(c(1, 2, 3, 4), nrow = 2),
  data_frame = data.frame(nombre = c("E. coli", "S. aureus"), gram = c("+", "-"))
)

print(compleja_lista)
```

## Diapositva de texto

Hola, esto es una prueba

## Imagen

[blablablabla](https://www.google.com/search?q=que+es+un+neutrofilo&oq=que+es+un+neutrofilo+&gs_lcrp=EgZjaHJvbWUyBggAEEUYOTIHCAEQIRiPAjIHCAIQIRiPAtIBCDM1OTVqMGo3qAIAsAIA&sourceid=chrome&ie=UTF-8)
